### 2016-08-17 ms/ms.tex
updated ms
First draft of the discussion

Using a long-term data-set of plant-pollinator communities assembling
following hedgerow restoration in the highly simplified and
intensively managed agricultural landscape of California's Central
Valley, we explore the process of network development. We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., changing points). Even with changing points in
interaction organization, networks could still be assembling via
preferential attachment if the network reorganizations were primarily
driven the by peripheral, temporally variable species while a stable,
well-connected core of species still persists. We thus examine whether
the species are most variable in their network position --- and thus
important contributors network reorganizations --- are less persistent
and connected species. %% interaction beta div, time beta div??
Lastly, we examine whether networks are assembling toward predictable
interaction patterns, and the ramifications for the robustness of the
networks to species extinction and perturbation.

@@

@@

We would like to thank Leto Peel and Aaron Clauset for their
invaluable discussions and for help with the change point analysis.
We thank the growers and land owners that allowed us to work on their
property.  We also greatly appreciate the identification assistance of
expert taxonomists Martin Hauser, Robbin Thorp and Jason Gibbs.  This
work was supported by funding from the Army Research Office
(W911NF-11-1-0361 to CK), the Natural Resources Conservation Service
(CIG-69-3A75-12-253, CIG-69-3A75-9-142, CIG-68-9104-6-101 and
WLF-69-7482-6-277 to The Xerces Society), the National Science
Foundation (DEB-0919128 to CK), The U.S.  Department of Agriculture
(USDA-NIFA 2012-51181-20105 to Michigan State University).  Funding
for LCP was provided by an NSF Graduate Research Fellowship and the
USDA NIFA Graduate Fellowship. FUNDING FOR MARILLIA.

>>>>

Using a long-term data-set of plant-pollinator communities assembling
following hedgerow restoration in the highly simplified and
intensively managed agricultural landscape of California's Central
Valley, we explore the process of network development. We first
determine whether the mechanism underlying network assembly is a
smooth build up of interactions as would be predicted by preferential
attachment, or punctuated by significant reorganizations of
interactions (i.e., changing points). Even with changing points in
interaction organization, networks could still be assembling via
preferential attachment if the network reorganizations were primarily
driven the by peripheral, temporally variable species while a stable,
well-connected core of species still persists. We thus examine whether
the species are most variable in their network position --- and thus
important contributors network reorganizations --- are less persistent
and connected species.  Lastly, we examine whether networks are
assembling toward predictable interaction patterns, and the
ramifications for the robustness of the networks to species extinction
and perturbation.

@@

We show that the temporal assembly of plant pollinator communities following restauration do not occur through preferential attachment. Instead, the community seems to undergo through a critical internal reorganization with major changes in species composition and interaction patterns.

Changing points through time = more in the assembling communities than in the control ones, as would be expected given the species turnover.

Preferential attachment is the most widely accepted theory explaining community assembly in mutualistic networks. Communities assembling through preferential attachment are formed by a core of generalist species, to which new species arriving to the comunity interact with. Thus, communities assembling through preferential attachmment exhibit an increase both in nestedness and in the overall level of species specialization, since specialist species are being added to the community. However, our changing point analysis results show that there is a critical reorganization in the interaction patterns as communities asssembly, which contradicts the preferential attatchment theory. Even though we encountered an increase in nestedness through time, specialization did not increase. Furthermore, this increase in nestedness could be explained by the increase in species richness. blablabla mechanistic models.

Other interesting result is that even though nestedness increased through time, modularity and connectance did not. \cite{Fortuna2010} suggest that at low connectance levels, mutualistic networks would present high nestedness and high modularity, while at high connectance levels networks would present low nestedness and low modularity. However, our results show the contrary: early communities presented low nestedness, smaller richness, and higher levels of modularity and connectance, while more mature communities presented higher nestedness, higher richness, and smaller modularity and connectance. SO blabla... XX Temporal overlap.

Evidence indicates that there is a positive relatioship between abundance and diet breadth, with the more generalist species having higher abundances. Because of the high generalism, species more abundat also present higher degrees. Thus, we expected that more generalist species would be part of the network core. Surprinsigly, the five most common species were also the ones that exhibited the most changes in interaction patterns. These species (names!) were always present in the periphery of the network. One hipothesys is that their high generalism allows them to explore the resources more boradly, allowing them to change their position in the network. XX mention the cloeseness variability and the species persistence.

High nestedness has been related to an increase in the robustnsess of comminities to species extinctions because the core of generalist species would act as a buffer against species loss (REF). Similarly, communities with greater modularity would be more robust in general, because modules would act as a buffer against perturbation spreading and the pervasive effects of species loss. We expected that as communities assemble and speceis richness incrase, communities would become increasingly robust to species loss. however, we found  that robustness to species loss did not change through time. This is interestingly from the conservation biology point of view, because even early assemblig communities seem to be as robust as more mature communites, despite the richness insurance hipothesis. However, communities are not only subjected to species loss, but also to other types of perturbations that can cascade through the network. Gaiarsa et al. (submitted) suggest useing algebraic connectivity to explore how vulnerable ecoogical communities might be to cascading effects. Our results indicate that more mature communities are more robust to cascading effects than early on assemblages, and that this result is related to species richness. This migth be related to XX....

@@

We would like to thank Leto Peel and Aaron Clauset for their
invaluable discussions and for help with the change point analysis.
We thank the growers and land owners that allowed us to work on their
property.  We also greatly appreciate the identification assistance of
expert taxonomists Martin Hauser, Robbin Thorp and Jason Gibbs.  This
work was supported by funding from the Army Research Office
(W911NF-11-1-0361 to CK), the Natural Resources Conservation Service
(CIG-69-3A75-12-253, CIG-69-3A75-9-142, CIG-68-9104-6-101 and
WLF-69-7482-6-277 to The Xerces Society), the National Science
Foundation (DEB-0919128 to CK), The U.S.  Department of Agriculture
(USDA-NIFA 2012-51181-20105 to Michigan State University).  Funding
for LCP was provided by an NSF Graduate Research Fellowship and the
USDA NIFA Graduate Fellowship. Funding for MPG was provided by Sao Paulo Research Foundation (FAPESP, grant 2013/13319-5).
